---
title: "RWorksheet_rocillo#1"
author: "Cassandra Jielin Rocillo"
date: "2024-09-04"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. How many data points?
+34 data points

```{r}
 age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50,37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
length(age)
```

2. Find the reciprocal of the values for age. 
```{r}
reciprocal_age <- 1 / age
library("MASS")
fractions(reciprocal_age)
```
3. Assign also new_age <- c(age, 0, age).
  What happen to the new_age?
```{r}
new_age <- c(age, 0, age)
new_age
```
4. Sort the values for age.
```{r}
sorted_age <- c(sort(age))
sorted_age
```

5.Find the minimum and maximum value for age. 
```{r}
min_age <- c(min(age))
max_age <- c(max(age))

print(min_age)
print(max_age)
```

6. How many data points
```{r}
  data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.7)
points <- length(data)
print(points)
```  


7. Generate a new vector for data where you double every value of the data. What happen to the data?
+The data were increased by two.
```{r}
double_data <-data*2

print(double_data)
```

8. Generate a sequence for the following scenario:
8.1 Integers from 1 to 100

```{r}
sequence_1to100 <- seq(1, 100)
print(sequence_1to100)
```

8.2 Numbers from 20 - 60
```{r}
 numbers_20to60 <- seq(20, 60)
print(numbers_20to60)
```

8.3 Mean of numbers from 20 to 60
```{r}
mean_number <- mean(seq(20, 60))
print(mean_number)
```

  
8.4 Sum of the numbers from 51 to 91
```{r}
numbers_sum <- sum(seq(51, 91))
print(numbers_sum)
```


8.5 Integers from 1 to 1,000
```{r}
sequence_1to100 <- 1:1000
print(sequence_1to100)
```

a. How many data points from 8.1 to 8.4
```{r}
l1 <- length(sequence_1to100)
l2 <- length(numbers_20to60)
l3 <- length(seq(20, 60))
l4 <- length(seq(51, 91))

total <- l1 + l2 + l3 + l4
print(total)
```


b. Write the R code and its output from 8.1 to 8.4 
```{r}
sequence_1to100 <- seq(1, 100)
numbers_20to60 <- seq(20,60)
mean_number <- mean(seq(20, 60))
numbers_sum <- sum(seq(51, 91))
```

c. For 8.5 find only maximum data points util 10
```{r}
max_util <- max(sequence_1to100[1:10])
print(max_util)
```
9. Print a vector with the integer between 1 and 100 tha are not divisible by 3, 5 and 7 using filter option.
```{r}
Filter(function(i) { all(i %% c(3, 5,7) != 0) }, seq(1, 100))

``` 


10. Generate a sequence backwards of the integeers  from 1 - 100
```{r}
backward <- seq(100, 1, by = -1)
print(backward)
```

11. List all the natural numbers below 25 that are multiples of 3 or 5. Find the sum of these multiples.
```{r}
numbers <- 1-25
multiples <- numbers[numbers %% 3 == 0 | numbers %% 5 == 0]
print(multiples)

sum <- sum(multiples)
print(sum)
```

12. Statements can be grouped together using braces'{' and '}'. A group of statements is sometimes called block. Single statements are evaluated when a new line is typed at the end of the syntactically complete statement. Blocks are not evaluated until a new line is entered after a closing braces. 
```{r}



```
Describe the output:
+An error occurred in my code.

13. Find x[2] and x[3]. 
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
x2 <- score[2]
x3 <- score[3]

print(x2)
print(x3)

```

14.
a. 
```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
print(a, na.print = "-999")

```
b. Describe the output.


15.Special type of function calls can appear on the left hand side of the assignment operator as in > class(x) <- "foo".
```{r}
name = readline=(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is", name, "and I am", age, "years old"))
print(R.version.string)
```


