---
title: "RWorksheet_rocillo#1"
author: "Cassandra Jielin Rocillo"
date: "2024-09-04"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. How many data points?
+34 data points

```{r}
 age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50,37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```

2. Find the reciprocal of the values for age. 
```{r}
reciprocal_age <- 1 / age
library("MASS")
fractions(reciprocal_age)
```
3. Assign also new_age <- c(age, 0, age).
  What happen to the new_age?
```{r}
new_age <- c(age, 0, age)
new_age
```
4. Sort the values for age.
```{r}
sorted_age <- c(sort(age))
sorted_age
```

5.Find the minimum and maximum value for age. 
```{r}
min_age <- c(min(age))
max_age <- c(max(age))

print(min_age)
print(max_age)
```

6. How many data points
```{r}
  data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.7)
points <- length(data)
print(points)
```  


7. Generate a new vector for data where you double every value of the data. What happen to the data?
+The data were increased by two.
```{r}
double_data <-data*2

print(double_data)
```

8. Generate a sequence for the following scenario:

8.1 Integers from 1 to 100.
```{r}
sequence <- seq(1, 100)
print(sequence)
```

8.2 Numbers from 20 - 60
```{r}
 n <- seq(20, 60)
print(n)
```

8.3 Mean of numbers from 20 to 60
```{r}
  number_Sequence <- seq(20, 60)

mean_number <- mean(number_Sequence)
print(mean_number)
```
8.4 Sum of the numbers from 51 to 91
```{r}
numbersum <- sum(seq(51-91))
numbersum
```


8.5 Integers from 1 to 1,000
```{r}
sequence <- 1:1000
print(sequence)
```

a. How manny data points from 8.1 to 8.4
```{r}
l1 <- length(sequence)
l2 <- length(numbers)
l3 <- length(mean_number)
l4 <- length(numbersum)

sum(l1 + l2 + l3 + l4)
```


b. Write the R code and its output from 8.1 to 8.4 
```{r}
sequence <- sequence(1:100)
```

